%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% License : MIT
% Link : https://www.overleaf.com/project/673c5b0f9f19c223b26dc03f
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-10pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-10pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeItemNoTitle}[1]{
  \item\small{
    {#1}
  }\vspace{-1pt}
}

\newcommand{\resumeItemSubitemNoTitle}[1]{
\begin{itemize}[label=\textbullet]
  \item{
    {#1}
  }\vspace{-1pt}
\end{itemize}
  
}

\newcommand{\tf}[1]{
    \textbf{#1}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item[]
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\experienceSubheading}[5]{
  \vspace{-1pt}\item[]
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} (#2) & #3 \\
      \textit{\small#4} & \textit{\small #5} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\projectSubheading}[5]{
  \vspace{-1pt}\item[]
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} (#5) & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\projectSubheadingWORef}[5]{
  \vspace{-1pt}\item[]
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]\vspace{4pt}}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://dreamhuan.github.io/}{\Large Kaiqi Fu}} 
  \\
  Mobile : +86-18268706984 \space\space\space\space\space\space\space \space\space   \space\space\space\space\space
  &
  Blog :\href{https://dreamhuan.github.io/}{ dreamhuan.github.io}
  & 
  Email : \href{mailto:fu\_kaiqi@qq.com}{fu\_kaiqi@qq.com}
  &
  GitHub : \href{https://github.com/dreamhuan}{github.com/dreamhuan}
  &
  Address : Hangzhou, Zhejiang
  \space
  \space\space
  
  
\end{tabular*}

\section{Experience}
  \resumeSubHeadingListStart
  
  \resumeSubheading
    {ByteDance}
    {Hangzhou, China}
    {Software Development Engineer}
    {Sept 2022 – Sept 2024}
    \resumeItemListStart
      \resumeItemNoTitle{
      Focused on business development for the Douyin Pay Merchant Portal platform—a ByteDance internal service platform designed for merchant onboarding and payment service integration.  
        \resumeItemSubitemNoTitle{
        Utilized the \textbf{Ract} tech stack alongside a \textbf{Go-based BFF} application layer for distributing RPC interface services.  
        }
        \resumeItemSubitemNoTitle{
        Refactored front-end logic using \textbf{Garfish} as the micro-frontend framework, enabling independent deployment of individual functional modules.  
        }
      } 
      \resumeItemNoTitle{
      Developed and maintained a role-based access control (RBAC) system to manage user permissions for the Merchant Portal platform. The core tech stack included Gulux (a full-stack development framework based on \textbf{Ract} and \textbf{Node.js}) and \textbf{MySQL}.  
      }
      \resumeItemNoTitle{
      Developed a form configuration platform based on the Formily framework to centralize the management of form logic for the Merchant Portal platform. This platform allows non-developers to preview and edit form fields while dynamically generating form configurations.  
      }
    \resumeItemListEnd  

  \resumeSubheading
    {Alibaba}
    {Hangzhou, China}
    {Software Development Engineer}
    {Jul 2021 – Sept 2022}
    \resumeItemListStart
      \resumeItemNoTitle{
      Worked as a front-end developer in Alibaba's community group-buying business, developing the sharing module for the Taocaicai App. The core tech stack included \textbf{Rax}, an internally developed cross-platform framework similar to \textbf{React}.  
      } 
      \resumeItemNoTitle{
      Developed a content platform for managing and distributing image and video assets, enabling users to share products more effectively and improve click-through rates. Utilized a tech stack including \textbf{Typescript}, \textbf{React}, and \textbf{Node.js}.  
      } 
      \resumeItemNoTitle{
      Developed a template platform for image composition, utilizing Alibaba's internal image synthesis service to add promotional information and other content to product images, aiming to enhance conversion rates for shared products.  
      } 
    \resumeItemListEnd  
  
  \resumeSubheading
    {Tuya Inc.}
    {Hangzhou, China}
    {Software Development Engineer}
    {May 2019 – Jul 2021}
    \resumeItemListStart
      \resumeItemNoTitle{
      Participated in design and development of IoT Platform Application Services using \textbf{Next.js} technology.  
      } 
      \resumeItemNoTitle{
      Developed a dependency management system to analyze project reference relationships, facilitating overall project migration and refactoring.  
      }
    \resumeItemListEnd  
  
    \resumeSubheading
      {Youzan Technology Ltd.}
      {Hangzhou, China}
      {Software Development Engineer}
      {Jul 2018 – Jan 2019}
      \resumeItemListStart
        \resumeItemNoTitle
        {Worked as an intern optimizing current features and building new features using \textbf{React}, \textbf{Vue} and \textbf{Node.js}.}
        \resumeItemNoTitle
        {Implemented a system to register components on the H5 side for rendering based on API responses. }
      \resumeItemListEnd

  \resumeSubHeadingListEnd



%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Hangzhou Normal University (HZNU)}{Hangzhou, China}
      {Bachelor of Engineering in Software Engineering}{Sept 2015 - Jul 2019}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Programming Skills}
  \resumeSubHeadingListStart
    \textbf{Programming Languages}{: Javascript, Typescript, Node.js, Java, Python, Go}
    \newline
    \textbf{Front-end Technology}{: React, Vue, Angular, Less, Scss, Redux, Bootstrap }
    \newline
    {\textbf{Back-end Development}}{: Express, Koa, MongoDB, MySQL, SpringBoot, Redis}
    \newline
    {\textbf{Devops}}{: Kubernetes, Docker, Alicloud, Bash }
    \newline
    \textbf{Tools}{: VSCode, Vim, Git, Iterm2, Oh-My-Zsh}
\resumeSubHeadingListEnd

\end{document}
